AFQ-Insight

### 2019-11-22 reports/manuscript/sections/conclusion.tex
More edits -- especially in methods, and a new section in conclusions.

>>>>

SGL has many other potential applications in neuroscience, because of the
hierarchical and grouped nature of many of the data -- that are collected in
multiple sample points within anatomically-defined areas. For example, this
method may be useful to understand the relationship between fMRI recordings and
behavior, where activity in each voxel may co-vary with voxels within the same
anatomical region and form features and groups of features. Similarly,
large-scale multi-electrode recordings of neural activity in awake behaving
animals are becoming increasingly feasible \cite{steinmetz2018distributed,
Jun2017-gv} and these recordings can form features (neurons) and groups (neurons
within an anatomical region). More ambitiously perhaps, this approach may be
used to understand the role of correlations in so-called resting-state fMRI
time-series and behavior, where pairwise correlations between voxels in
different anatomical regions are features in the matrix and features may be
grouped by pairs of anatomical regions. Given the large number of voxels in the
surface of the gray matter, and given that correlations increase the number of
features by a factor of $n^2$ this would be a challenging problem to solve using
SGL.
